---
title: 'Kaggle - House Price Prediction - Feature Exploration'
date: '`r Sys.Date()`'
output:
  html_document:
    number_sections: true
    fig_caption: true
    toc: true
    fig_width: 8.75
    fig_height: 5.65
    theme: cosmo
    highlight: tango
    code_folding: hide
---
# Introduction
Ask a home buyer to describe their dream house, and they probably won't begin with the height of the basement ceiling or the proximity to an east-west railroad. But this playground competition's dataset proves that much more influences price negotiations than the number of bedrooms or a white-picket fence.

With 79 explanatory variables describing (almost) every aspect of residential homes in Ames, Iowa, this competition challenges to predict the final price of each home.

This kernel aims at exploration of each 79 features.

## Loading all Required libraries
- **Rmisc** : For multiplot function
- **ggplot2,ggforce, corrplot** : For plots
- **dplyr, tidyr** : For data operations
- **data.table** : For Loading Data
- **knitr** : To kneet html
```{r warning = FALSE, error = FALSE, results='hide', message=FALSE}
library(Rmisc)
library(ggplot2)
library(ggforce)
library(dplyr)
library(tidyr)
library(data.table)
library(knitr)
library(corrplot)
```

## Functions to plot factor and continous variables
Creating common function using ggplot and multiplot to explore factor features and continous numeric features. This function will take three arguments - dataframe, x variable and y variable(target).

* **factorchart** : Returns three charts : boxplot, bar chart for count and bar chart for mean of target
* **contChart**   : Returns two charts   : histogram + density, scatter plot against target with linear regression and standard error
```{r warning = FALSE, error = FALSE, results='hide', message=FALSE}
factorChart <- function (df, val1, val2) {
  p1 <- ggplot(df, aes(x = as.factor(df[[val1]]), y = df[[val2]], fill =  as.factor(df[[val1]]))) +
    geom_boxplot() +
    theme(legend.position = "none") +
    labs(x = "", y = val2)+
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    scale_y_continuous(labels = scales::comma)
  
  p2 <- ggplot(df, aes(x = as.factor(df[[val1]]), fill =  as.factor(df[[val1]]))) +
    geom_bar() +
    geom_text(stat = "count", aes(label =..count..), vjust = -0.5) +
    theme(legend.position = "none")+
    labs(x = val1)+
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) 
  
  p3 <- ggplot(df, aes(x = as.factor(df[[val1]]), y = df[[val2]],  fill =  as.factor(df[[val1]]))) +
    geom_bar(stat = "summary", fun.y = "mean") +
    theme(legend.position = "none")+
    labs(x = val1, y = "Mean") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    scale_y_continuous(labels = scales::comma)
  
  
  layout <- matrix(c(1,1,1,1,2,2,3,3),2,4,byrow=TRUE)
  multiplot(p1, p2, p3, layout=layout)  
}

contChart <- function (df, val1, val2) {
p1 <- ggplot(df, aes(x = train[[val1]], y = ..density..)) +
      geom_histogram(fill = "red", alpha = 0.2, color = "black") +
      geom_density(fill = "green", alpha = 0.2)+
      labs(x = val1)

p2 <- ggplot(df, aes(x = df[[val1]], y = df[[val2]])) +
      geom_point(color = "red", alpha = 0.3) +
      geom_smooth(method = "lm")+
    labs(x = val1, y = val2)+
    scale_y_continuous(labels = scales::comma)

layout <- matrix(c(1,2), 1, 2, byrow=TRUE)
multiplot(p1, p2, layout=layout)
}
```

## Load Data
We are using **fread** function to read train and test csv files. fread is easiest and one of the most powerful function to load data(except excel)
```{r}
#setwd("D:/Kaggle/House Prices Advanced Regression Techniques")
setwd("..//input/")
train <- fread("train.csv", stringsAsFactors = TRUE)
test <- fread("test.csv", stringsAsFactors = TRUE)
```

## Data Overview
Let's look at few sample records first
```{r}
kable(head(train))
```

Train got 1460 observations and 81 variables. Test got 80 variables(excluding target variable - SalePrice)

## Missing Values
Let's look at columns with some missing values
```{r warning = FALSE}
train_nulls <- as.data.frame(colSums(is.na(train)))#as.data.frame(sapply(X = train, FUN = function(x) sum(is.na(x))))
train_nulls <- add_rownames(train_nulls, "Column")
colnames(train_nulls)[2] <- "nulls"
train_nulls$notNulls = nrow(train) - train_nulls$nulls

train_nulls %>%
  filter(nulls > 0) %>%
  gather("null_flag", "count", -Column) %>%
  ggplot(aes(x = Column, y = count, fill = null_flag)) +
  geom_bar(stat = "identity",position = "fill") +
  theme(legend.position = "bottom") +
  coord_flip()
```


Few features get almost 100% null values. e.g. poolqc. Probably null poolqc means no pool. It will lbe meaningful. We will impute null values after exploring each feature


## Exploring Each Feature
### MSSubClass
As per data dictonary:

**MSSubClass:** Identifies the type of dwelling involved in the sale.	

        20	1-STORY 1946 & NEWER ALL STYLES
        30	1-STORY 1945 & OLDER
        40	1-STORY W/FINISHED ATTIC ALL AGES
        45	1-1/2 STORY - UNFINISHED ALL AGES
        50	1-1/2 STORY FINISHED ALL AGES
        60	2-STORY 1946 & NEWER
        70	2-STORY 1945 & OLDER
        75	2-1/2 STORY ALL AGES
        80	SPLIT OR MULTI-LEVEL
        85	SPLIT FOYER
        90	DUPLEX - ALL STYLES AND AGES
       120	1-STORY PUD (Planned Unit Development) - 1946 & NEWER
       150	1-1/2 STORY PUD - ALL AGES
       160	2-STORY PUD - 1946 & NEWER
       180	PUD - MULTILEVEL - INCL SPLIT LEV/FOYER
       190	2 FAMILY CONVERSION - ALL STYLES AND AGES

Although we read it as integer but it is actually a factor. 

```{r}
factorChart(train, "MSSubClass", "SalePrice")
```

**Conclusion:** Looks promosing feature with clear distinction between top 2 categories - 1 story and 2 story

### MSZoning
As per data dictonary:
**MSZoning:** Identifies the general zoning classification of the sale.
		
       A	Agriculture
       C	Commercial
       FV	Floating Village Residential
       I	Industrial
       RH	Residential High Density
       RL	Residential Low Density
       RP	Residential Low Density Park 
       RM	Residential Medium Density

```{r}
factorChart(train, "MSZoning", "SalePrice")
```

**Conclusion:** Most of the values belong to Residential low and medium density. Boxplot also suggest good distinction between those. Mean too suggests same thing. Good Feature.

### LotFrontage
**LotFrontage:** Linear feet of street connected to property.

```{r warning = FALSE, error = FALSE, message=FALSE}
contChart(train, "LotFrontage", "SalePrice")
```

**Conclusion:** Most of the frountage values are between 0 to 100. Good linear relation ship with target variable.

### LotArea
**LotArea:** Lot size in square feet - Probably most important feature. Let's check


```{r}
contChart(train, "LotArea", "SalePrice")
```
Unfortunately our custom made function not giving valuable information due to outliers. Let's try again by zooming desne values.
```{r}
train %>%
  ggplot(aes(x = LotArea)) +
  geom_histogram(color = "red", binwidth = 100) +
  facet_zoom(x = (LotArea >0 & LotArea < 20000))
  
```

```{r}
train %>%
  ggplot(aes(x = LotArea, y = SalePrice)) +
      geom_point(color = "red", alpha = 0.3) +
      geom_smooth(method = "lm")+
    scale_y_continuous(labels = scales::comma)+
  facet_zoom(x = (LotArea >0 & LotArea < 50000))
```

**Conclusion:** Most of values are between 5000 and 15000. Strong linear relation with target variable.

### Street
**Street:** Type of road access to property

       Grvl	Gravel	
       Pave	Paved


```{r}
factorChart(train, "Street", "SalePrice")
```

**Conclusion:** Almost all values belong to Pave streets. Not useful.

### Alley
**Alley:** Type of alley access to property

       Grvl	Gravel
       Pave	Paved
       NA 	No alley access
```{r}
factorChart(train, "Alley", "SalePrice")
```
**Conclusion:** Most of the homes are with no Alley. Acutally we can impute NA with some meaningful value.

### LotShape
**LotShape:** General shape of property

       Reg	Regular	
       IR1	Slightly irregular
       IR2	Moderately Irregular
       IR3	Irregular


```{r}
factorChart(train, "LotShape", "SalePrice")
```

** Conclusion :** Moderately Irregular lot should fetch lesser price than slightly irregular lot. However it is not the case here. Probably because IR2 and IR3 got very small number of observations. It is also possible that Lotsize masking this fact. So let's use prize per square feet instead of SalePrice.
```{r}
train$psf <- train$SalePrice / train$LotArea
```

###LandContour
**LandContour:** Flatness of the property

       Lvl	Near Flat/Level	
       Bnk	Banked - Quick and significant rise from street grade to building
       HLS	Hillside - Significant slope from side to side
       Low	Depression


```{r}
factorChart(train, "LandContour", "psf")
```

**Conclusion:** Most of the houses are near flat. Ofcourse Hill side got more value than depression one.

###Utilities
**Utilities:** Type of utilities available
		
		   AllPub	All public Utilities (E,G,W,& S)	
       NoSewr	Electricity, Gas, and Water (Septic Tank)
       NoSeWa	Electricity and Gas Only
       ELO	Electricity only	

```{r}
factorChart(train, "Utilities", "psf")
```
**Conclusion:** Not at all useful. Very much skewed. Almost all house got all publice utilities except one.

###LotConfig: 
**Lot configuration:**

       Inside	Inside lot
       Corner	Corner lot
       CulDSac	Cul-de-sac
       FR2	Frontage on 2 sides of property
       FR3	Frontage on 3 sides of property

```{r}
factorChart(train, "LotConfig", "psf")
```
**Conclusion:** Not much to distinguish between Inside and corner. FR3 fetches good price ofcourse. But not enough values to conclude anything.

###LandSlope
**LandSlope:** 
       Slope of property
       Gtl	Gentle slope
       Mod	Moderate Slope	
       Sev	Severe Slope
```{r}
factorChart(train, "LandSlope", "psf")
```
**Conclusion: ** Probably realted with LandContour. gtl > mode > sev justified

###Neighborhood
**Neighborhood:** Physical locations within Ames city limits

       Blmngtn	Bloomington Heights
       Blueste	Bluestem
       BrDale	Briardale
       BrkSide	Brookside
       ClearCr	Clear Creek
       CollgCr	College Creek
       Crawfor	Crawford
       Edwards	Edwards
       Gilbert	Gilbert
       IDOTRR	Iowa DOT and Rail Road
       MeadowV	Meadow Village
       Mitchel	Mitchell
       Names	North Ames
       NoRidge	Northridge
       NPkVill	Northpark Villa
       NridgHt	Northridge Heights
       NWAmes	Northwest Ames
       OldTown	Old Town
       SWISU	South & West of Iowa State University
       Sawyer	Sawyer
       SawyerW	Sawyer West
       Somerst	Somerset
       StoneBr	Stone Brook
       Timber	Timberland
       Veenker	Veenker
```{r}
factorChart(train, "Neighborhood", "psf")
```
**Conclusion:** Few neighborhood will be better. Looks important feature. We will explore it more at time of model creation.

###Condition1 ###
**Condition1:** Proximity to various conditions
	

       Artery	Adjacent to arterial street
       Feedr	Adjacent to feeder street	
       Norm	Normal	
       RRNn	Within 200' of North-South Railroad
       RRAn	Adjacent to North-South Railroad
       PosN	Near positive off-site feature--park, greenbelt, etc.
       PosA	Adjacent to postive off-site feature
       RRNe	Within 200' of East-West Railroad
       RRAe	Adjacent to East-West Railroad
```{r}
factorChart(train, "Condition1", "psf")
```
**Conclustion:** People don't like building adjacent to rail roads or streets.

###Condition2###
**Condition2:** Proximity to various conditions (if more than one is present)
       
       Artery	Adjacent to arterial street
       Feedr	Adjacent to feeder street	
       Norm	Normal	
       RRNn	Within 200' of North-South Railroad
       RRAn	Adjacent to North-South Railroad
       PosN	Near positive off-site feature--park, greenbelt, etc.
       PosA	Adjacent to postive off-site feature
       RRNe	Within 200' of East-West Railroad
       RRAe	Adjacent to East-West Railroad
```{r}
factorChart(train, "Condition2", "psf")
```
**Conclusion: ** Need to mix it with condition 1 to get better result

###BldgType ###
**BldgType:** Type of dwelling
		
>       1Fam	Single-family Detached	
>       2FmCon	Two-family Conversion; originally built as one-family dwelling
>       Duplx	Duplex
>       TwnhsE	Townhouse End Unit
>       TwnhsI	Townhouse Inside Unit

```{r}
factorChart(train, "BldgType", "psf")
```
**Conclusion :** Superb Feature. Twinhouse definetly fetching higher price than others

### HouseStyle###
**HouseStyle:** Style of dwelling
	
       1Story	One story
       1.5Fin	One and one-half story: 2nd level finished
       1.5Unf	One and one-half story: 2nd level unfinished
       2Story	Two story
       2.5Fin	Two and one-half story: 2nd level finished
       2.5Unf	Two and one-half story: 2nd level unfinished
       SFoyer	Split Foyer
       SLvl	Split Level
```{r}
factorChart(train, "HouseStyle", "psf")
```
**Conclusion : **2 story getting premium prize

###OverallQual###
**OverallQual:** Rates the overall material and finish of the house

       10	Very Excellent
       9	Excellent
       8	Very Good
       7	Good
       6	Above Average
       5	Average
       4	Below Average
       3	Fair
       2	Poor
       1	Very Poor

```{r}
factorChart(train, "OverallQual", "psf")
```

```{r}
factorChart(train, "OverallQual", "SalePrice")
```
**Conclusion:** Definetly a decider. Possibaly most important feature.Also it suggests good quality houses are spacious. 

###OverallCond###
**OverallCond:** Rates the overall condition of the house

       10	Very Excellent
       9	Excellent
       8	Very Good
       7	Good
       6	Above Average	
       5	Average
       4	Below Average	
       3	Fair
       2	Poor
       1	Very Poor
```{r}
factorChart(train, "OverallCond", "SalePrice")
```

```{r}
factorChart(train, "OverallCond", "psf")
```
**Conclusion:** 5 is fetching higher price than 6,7,8. Interesting? Need to explore more. 

###YearBuilt###
**YearBuilt:** Original construction date
```{r}
contChart(train, "YearBuilt", "SalePrice")
```
**Conclusion :**Definetly latest home taking more prize. We can define new continous variable HouseAge

###YearRemodAdd###
**YearRemodAdd:** Remodel date (same as construction date if no remodeling or additions)
```{r}
contChart(train, "YearRemodAdd", "SalePrice")
```
let's also find out if house is remodeled or not
```{r}
train %>%
  mutate(remodel_flag = ifelse(YearBuilt == YearRemodAdd, "N", "Y")) %>%
  group_by(remodel_flag) %>%
  dplyr::summarize(count = n(),
            avg = mean(psf),
            median = median(psf))

train %>%
  mutate(remodel_flag = ifelse(YearBuilt == YearRemodAdd, "N", "Y")) %>%
  ggplot(aes(x = remodel_flag, y = psf, fill = remodel_flag)) +
  geom_boxplot()
```

```{r}
train %>%
  mutate(remodel_flag = ifelse(YearBuilt == YearRemodAdd, "N", "Y")) %>%
  filter(remodel_flag == "Y") %>%
  ggplot(aes(x = YearRemodAdd, y = psf, fill = YearBuilt)) +
    geom_bar(stat = "identity")
```
**Conclusion:** What happended in 1950?

###RoofStyle###
**RoofStyle:** Type of roof

       Flat	Flat
       Gable	Gable
       Gambrel	Gabrel (Barn)
       Hip	Hip
       Mansard	Mansard
       Shed	Shed

```{r}
factorChart(train, "RoofStyle", "psf")
```
**Conclusion :** Pass. Nothing to differentiate between top 2 values.

###RoofMatl###
**RoofMatl:** Roof material

       ClyTile	Clay or Tile
       CompShg	Standard (Composite) Shingle
       Membran	Membrane
       Metal	Metal
       Roll	Roll
       Tar&Grv	Gravel & Tar
       WdShake	Wood Shakes
       WdShngl	Wood Shingles

```{r}
factorChart(train, "RoofMatl", "psf")
```
**Conclusion :** Again most of the values belong to one category only 

###Exterior1st###
**Exterior1st:** Exterior covering on house

       AsbShng	Asbestos Shingles
       AsphShn	Asphalt Shingles
       BrkComm	Brick Common
       BrkFace	Brick Face
       CBlock	Cinder Block
       CemntBd	Cement Board
       HdBoard	Hard Board
       ImStucc	Imitation Stucco
       MetalSd	Metal Siding
       Other	Other
       Plywood	Plywood
       PreCast	PreCast	
       Stone	Stone
       Stucco	Stucco
       VinylSd	Vinyl Siding
       Wd Sdng	Wood Siding
       WdShing	Wood Shingles
```{r}
factorChart(train, "Exterior1st", "psf")
```
**Conclusion :** Interestign feature

###Exterior2nd###
**Exterior2nd:** Exterior covering on house (if more than one material)

       AsbShng	Asbestos Shingles
       AsphShn	Asphalt Shingles
       BrkComm	Brick Common
       BrkFace	Brick Face
       CBlock	Cinder Block
       CemntBd	Cement Board
       HdBoard	Hard Board
       ImStucc	Imitation Stucco
       MetalSd	Metal Siding
       Other	Other
       Plywood	Plywood
       PreCast	PreCast
       Stone	Stone
       Stucco	Stucco
       VinylSd	Vinyl Siding
       Wd Sdng	Wood Siding
       WdShing	Wood Shingles

```{r}
factorChart(train, "Exterior2nd", "psf")
```
**Conclusion:** Exterior 2nd is equal to 1st if both exterior are same.Need to create some other feature around it.

###MasVnrType###
**MasVnrType:** Masonry veneer type

       BrkCmn	Brick Common
       BrkFace	Brick Face
       CBlock	Cinder Block
       None	None
       Stone	Stone

```{r}
factorChart(train, "MasVnrType", "psf")
```
**Conclusion:** Need to replace null values with none.

###MasVnrArea###
**MasVnrArea:** Masonry veneer area in square feet
```{r error=FALSE, warning=FALSE, message=FALSE}
contChart(train, "MasVnrArea", "psf")
```

```{r error=FALSE, warning=FALSE, message=FALSE}
contChart(train, "MasVnrArea", "SalePrice")
```
**Conclusion:** most of the value are 0

###ExterQual###
ExterQual: Evaluates the quality of the material on the exterior 
		
       Ex	Excellent
       Gd	Good
       TA	Average/Typical
       Fa	Fair
       Po	Poor

```{r}
factorChart(train, "ExterQual", "psf")
```
**Conclusion :** Excellent feature. Clear distinction between top 2 values - Good and Average

###ExterCond###
**ExterCond:** Evaluates the present condition of the material on the exterior
		
       Ex	Excellent
       Gd	Good
       TA	Average/Typical
       Fa	Fair
       Po	Poor

```{r}
factorChart(train, "ExterCond", "psf")
```
**Conclusion :** Nope.

###Foundation###
**Foundation:** Type of foundation
		
       BrkTil	Brick & Tile
       CBlock	Cinder Block
       PConc	Poured Contrete	
       Slab	Slab
       Stone	Stone
       Wood	Wood
```{r}
factorChart(train, "Foundation", "psf")
```
**Conclusion :** Nice One! Clear distinction between top 2 values

###BsmtCond###
**BsmtCond:** Evaluates the general condition of the basement

       Ex	Excellent
       Gd	Good
       TA	Typical - slight dampness allowed
       Fa	Fair - dampness or some cracking or settling
       Po	Poor - Severe cracking, settling, or wetness
       NA	No Basement

```{r}
factorChart(train, "BsmtCond", "psf")
```
**Conclusion :** Again superb picture. Nice distinction between top 3 values 

###BsmtExposure###
**BsmtExposure:** Refers to walkout or garden level walls

       Gd	Good Exposure
       Av	Average Exposure (split levels or foyers typically score average or above)	
       Mn	Mimimum Exposure
       No	No Exposure
       NA	No Basement
```{r}
factorChart(train, "BsmtExposure", "psf")
```
**Conclusion: ** No clear distinction

###BsmtFinType1###
***BsmtFinType1:*** Rating of basement finished area

       GLQ	Good Living Quarters
       ALQ	Average Living Quarters
       BLQ	Below Average Living Quarters	
       Rec	Average Rec Room
       LwQ	Low Quality
       Unf	Unfinshed
       NA	No Basement
```{r}
factorChart(train, "BsmtFinType1", "psf")
```

```{r}
factorChart(train, "BsmtFinType1", "SalePrice")
```
**Conclusion:** Not bad

###BsmtFinSF1###
**BsmtFinSF1:** Type 1 finished square feet
```{r warning = FALSE, error = FALSE, message=FALSE}
contChart(train, "BsmtFinSF1", "psf")
```
**Conclusion:** Many values without basement and quite a few outlier. Below Average feature

###BsmtFinType2###
**BsmtFinType2:** Rating of basement finished area (if multiple types)

       GLQ	Good Living Quarters
       ALQ	Average Living Quarters
       BLQ	Below Average Living Quarters	
       Rec	Average Rec Room
       LwQ	Low Quality
       Unf	Unfinshed
       NA	No Basement
```{r}
factorChart(train, "BsmtFinType2", "psf")
```
**Conclusion:** Most of the value belong to one category only. Not helpful.

###BsmtFinSF2###
**BsmtFinSF2:** Type 2 finished square feet
```{r warning = FALSE, message=FALSE, error=FALSE}
contChart(train, "BsmtFinSF2", "psf")
```

Need to create new feature whether 2nd basement is present or not. Looks like all 0 are not having 2nd basement.
```{r}
train %>%
  mutate(bsmt2Flag = ifelse(BsmtFinSF2 == 0, "N", "Y")) %>%
  factorChart("bsmt2Flag", "psf")
```
**Conclusion:** 2nd basement not helping much.

###BsmtUnfSF###
**BsmtUnfSF:** Unfinished square feet of basement area
```{r warning = FALSE, message=FALSE, error=FALSE}
contChart(train, "BsmtUnfSF", "psf")
```
**Conclusion:** Very neutral feature.

###TotalBsmtSF###
**TotalBsmtSF:** Total square feet of basement area
```{r warning = FALSE, message=FALSE, error=FALSE}
contChart(train, "TotalBsmtSF", "psf")
```
Very strong relationship. Let's zoom dense area
```{r}
train %>%
  ggplot(aes(x = TotalBsmtSF, y = psf)) +
      geom_point(color = "red", alpha = 0.3) +
      geom_smooth(method = "lm")+
    scale_y_continuous(labels = scales::comma)+
  facet_zoom(x = (TotalBsmtSF >0 & TotalBsmtSF < 3000))
```
**Conclusion: ** Nice one!!

###Heating###
**Heating:** Type of heating
		
       Floor	Floor Furnace
       GasA	Gas forced warm air furnace
       GasW	Gas hot water or steam heat
       Grav	Gravity furnace	
       OthW	Hot water or steam heat other than gas
       Wall	Wall furnace
```{r}
factorChart(train, "Heating", "psf")
```
**Conclusion: ** Almost all houses got Gas forced warm air furnace except 32. This wouldn't help much.

###HeatingQC###
**HeatingQC:** Heating quality and condition

       Ex	Excellent
       Gd	Good
       TA	Average/Typical
       Fa	Fair
       Po	Poor
```{r}
factorChart(train, "HeatingQC", "psf")
```

```{r}
factorChart(train, "HeatingQC", "SalePrice")
```
**Conclusion: ** Superb. However I think it must be highly co-related with overall rating.

###CentralAir###
**CentralAir:** Central air conditioning

       N	No
       Y	Yes
```{r}
factorChart(train, "CentralAir", "SalePrice")
```
**Conclustion :** Most of the values belong to one category

###Electrical###
**Electrical:** Electrical system

       SBrkr	Standard Circuit Breakers & Romex
       FuseA	Fuse Box over 60 AMP and all Romex wiring (Average)	
       FuseF	60 AMP Fuse Box and mostly Romex wiring (Fair)
       FuseP	60 AMP Fuse Box and mostly knob & tube wiring (poor)
       Mix	Mixed

```{r}
factorChart(train, "Electrical", "psf")
```
***Conclusion:*** Practically I don't think electrical system can affect price. However it is possible SBrkr is new system and that is why higher mean?

###1stFlrSF###
**1stFlrSF:** First Floor square feet
```{r message= FALSE}
contChart(train, "1stFlrSF", "psf")
```

```{r message= FALSE}
contChart(train, "1stFlrSF", "SalePrice")
```
**Conclusion:** Higher the squarefeet of 1st floor, higher the price

###2ndFlrSF###
**2ndFlrSF:** Second floor square feet
```{r message= FALSE}
contChart(train, "2ndFlrSF", "SalePrice")
```
Many houses doesnt have 2nd floor. So let's filter them out.
```{r}
train %>%
  filter(`2ndFlrSF` > 0) %>%
  ggplot(aes(x = `2ndFlrSF`, y = SalePrice)) +
  geom_point(color = "red", alpha = 0.3) +
  geom_smooth(method = "lm")
```
**Conclusion :** Ahh!! You can't find more linear relationship than this ;)

###LowQualFinSF###
**LowQualFinSF:** Low quality finished square feet (all floors)

```{r message = FALSE}
contChart(train, "LowQualFinSF", "psf")
```
Very less house with any low quality finishing. Let's check it out
```{r}
train %>%
  mutate(LowQualFlag = ifelse(LowQualFinSF > 0, 1, 0)) %>%
  group_by(LowQualFlag) %>%
  dplyr::summarize(avg = mean(psf),
            cnt = n(),
            avgSP = mean(SalePrice)) %>%
  ggplot(aes(x = as.factor(LowQualFlag), y = cnt, fill = as.factor(LowQualFlag))) +
    geom_bar(stat = "identity")
  
```
***Conclusion:*** Very less number of buildings there. 

###GrLivArea###
**GrLivArea:** Above grade (ground) living area square feet
```{r message=FALSE}
contChart(train, "GrLivArea", "SalePrice")
```

```{r message = FALSE}
contChart(train, "GrLivArea", "psf")
```
**Conclusion : ** Very similar to other area features

###BsmtFullBath###
**BsmtFullBath**: Basement full bathrooms

```{r}
factorChart(train,"BsmtFullBath", "psf")
```

```{r}
factorChart(train,"BsmtFullBath", "SalePrice")
```
**Conclusion :** more than 0 bathroom definetly helps fetching more prize

###BsmtHalfBath###
**BsmtHalfBath:** Basement half bathrooms
```{r}
factorChart(train,"BsmtHalfBath", "psf")
```
**Conclusion : ** Very less number of house got more than half bath. Nothing conclusive here.

###FullBath:###
**FullBath:** Full bathrooms above grade
```{r}
factorChart(train, "FullBath", "psf")
```
**Conclusion :** Clear distinction between 1 and 2 bath. Nice One!!!

###HalfBath###
**HalfBath:** Half baths above grade

```{r}
factorChart(train, "HalfBath", "SalePrice")
```
**Conclusion :** I think adding this with FullBath will give better feature.

###Bedroom###
**Bedroom:** Bedrooms above grade (does NOT include basement bedrooms)
```{r}
factorChart(train, "BedroomAbvGr", "psf")
```

```{r}
factorChart(train, "BedroomAbvGr", "SalePrice")
```
**Conclusion: ** Although 3 and 4 bedroom will fetch more prize, but psf will not be better

###Kitchen###
**Kitchen:** Kitchens above grade
```{r}
factorChart(train, "KitchenAbvGr", "psf")
```
**Conclusion :** Most of the home got 1 kitchen. Not helpful.

###KitchenQual###
**KitchenQual:** Kitchen quality

       Ex	Excellent
       Gd	Good
       TA	Typical/Average
       Fa	Fair
       Po	Poor

```{r}
factorChart(train, "KitchenQual", "psf")
```
**Conclusion: ** Expected. Nice Feature.

###TotRmsAbvGrd###
**TotRmsAbvGrd:** Total rooms above grade (does not include bathrooms)

```{r}
factorChart(train, "TotRmsAbvGrd", "psf")
```

```{r}
factorChart(train, "TotRmsAbvGrd", "SalePrice")
```
**Conclusion: ** Definetley key feature.

###Functional###
**Functional:** Home functionality (Assume typical unless deductions are warranted)

       Typ	Typical Functionality
       Min1	Minor Deductions 1
       Min2	Minor Deductions 2
       Mod	Moderate Deductions
       Maj1	Major Deductions 1
       Maj2	Major Deductions 2
       Sev	Severely Damaged
       Sal	Salvage only

```{r}
factorChart(train, "Functional", "SalePrice")
```
***Conclusion:*** Most of the houses are having typical functionality only. Not helpful.

###Fireplaces###
**Fireplaces:** Number of fireplaces
```{r}
factorChart(train, "Fireplaces", "psf")
```

```{r}
factorChart(train, "Fireplaces", "SalePrice")
```

**Conclusion:** Usually big houses got fireplace as psf not increasing with Fireplaces.

###FireplaceQu###
**FireplaceQu:** Fireplace quality

       Ex	Excellent - Exceptional Masonry Fireplace
       Gd	Good - Masonry Fireplace in main level
       TA	Average - Prefabricated Fireplace in main living area or Masonry Fireplace in basement
       Fa	Fair - Prefabricated Fireplace in basement
       Po	Poor - Ben Franklin Stove
       NA	No Fireplace

```{r}
factorChart(train, "FireplaceQu" ,"psf")
```
**Conclusion: ** If fireplace exists than there is good co-relation.

###GarageType###
**GarageType:** Garage location
		
       2Types	More than one type of garage
       Attchd	Attached to home
       Basment	Basement Garage
       BuiltIn	Built-In (Garage part of house - typically has room above garage)
       CarPort	Car Port
       Detchd	Detached from home
       NA	No Garage
```{r}
factorChart(train, "GarageType", "psf")
```

```{r}
factorChart(train, "GarageType", "SalePrice")
```
**Conclusion:** Attached are better than detached.

###GarageYrBlt###
**GarageYrBlt:** Year garage was built

```{r warning = FALSE, message=FALSE}
contChart(train, "GarageYrBlt", "psf")
```

```{r warning = FALSE, message=FALSE}
contChart(train, "GarageYrBlt", "SalePrice")
```
**Conclusion :** Most of the garages are built between 2000 and 2010. It also fetches more prize.

###GarageFinish###
**GarageFinish:** Interior finish of the garage

       Fin	Finished
       RFn	Rough Finished	
       Unf	Unfinished
       NA	No Garage
```{r}
factorChart(train, "GarageFinish", "psf")
```
**Conclusion  : ** Wow!! clear differnce :)

###GarageCars###
**GarageCars:** Size of garage in car capacity
```{r}
factorChart(train, "GarageCars", "psf")
```
**Conclusion : ** It seems Garrage is very important feature while buying house.

###GarageArea###
**GarageArea:** Size of garage in square feet

```{r message = FALSE}
contChart(train, "GarageArea", "psf")
```

```{r message=FALSE}
contChart(train, "GarageArea", "SalePrice")
```
**Conclusion :** Nice linearity.

###GarageQual###
**GarageQual:** Garage quality

       Ex	Excellent
       Gd	Good
       TA	Typical/Average
       Fa	Fair
       Po	Poor
       NA	No Garage
       
```{r}
factorChart(train, "GarageQual", "psf")
```
**Conclusion :** Most of the garages are average. Not useful.

###GarageCond###
**GarageCond:** Garage condition

       Ex	Excellent
       Gd	Good
       TA	Typical/Average
       Fa	Fair
       Po	Poor
       NA	No Garage
```{r}
factorChart(train, "GarageCond", "psf")
```
**Conclusion : ** Not helpful

###PavedDrive###
**PavedDrive:** Paved driveway

       Y	Paved 
       P	Partial Pavement
       N	Dirt/Gravel
```{r}
factorChart(train, "PavedDrive", "psf")
```
**Conclusion : ** House with Paved Drive are better

###WoodDeckSF###
**WoodDeckSF:** Wood deck area in square feet

```{r message=FALSE}
contChart(train, "WoodDeckSF", "psf")
```

Most of the houses doesn't having wood deck. So let's consider house wiht wood deck only.
```{r message = FALSE}
train %>%
  filter(WoodDeckSF > 0) %>%
  ggplot(aes(x = WoodDeckSF, y = SalePrice)) +
  geom_point(col = "red", alpha = 0.2) +
  geom_smooth(method = "lm")
```
**Conculusion :** Nice Feature.

###OpenPorchSF###
**OpenPorchSF:** Open porch area in square feet

```{r message=FALSE}
contChart(train, "OpenPorchSF", "psf")
```
Let's create scatter plot for only greater than 0 porches.
```{r}
train %>%
  filter(OpenPorchSF > 0) %>%
  ggplot(aes(x = OpenPorchSF, y = SalePrice)) +
  geom_point(col = "red", alpha = 0.2) +
  geom_smooth(method = "lm")
```
**Conclusion : ** Not so much linear. 

###EnclosedPorch###
**EnclosedPorch:** Enclosed porch area in square feet

```{r message =FALSE}
contChart(train, "EnclosedPorch", "psf")
```

```{r}
train %>%
  filter(EnclosedPorch > 0) %>%
  ggplot(aes(x = EnclosedPorch, y = psf)) +
  geom_point(col = "red", alpha = 0.2) +
  geom_smooth(method = "lm")
```
**Conclusion : ** Nothing interesting from first glance.

###3SsnPorch###
**3SsnPorch:** Three season porch area in square feet
```{r}
train %>%
  filter(`3SsnPorch` > 0) %>%
  ggplot(aes(x = `3SsnPorch`, y = psf)) +
  geom_point(col = "red", alpha = 0.2) +
  geom_smooth(method = "lm")
```
Conclusion : Very less house with more than 0. Can be ignored.

###ScreenPorch###
**ScreenPorch:** Screen porch area in square feet
```{r}
train %>%
  filter(ScreenPorch > 0) %>%
  ggplot(aes(x = ScreenPorch, y = SalePrice)) +
  geom_point(col = "red", alpha = 0.2) +
  geom_smooth(method = "lm")
```
**Conclusion :** Not much impact on final price

###PoolArea###
**PoolArea:** Pool area in square feet
```{r message = FALSE}
contChart(train, "PoolArea", "psf")
```

**Conclusion : ** only 7 houses with pool.

###PoolQC###
**PoolQC:** Pool quality
		
       Ex	Excellent
       Gd	Good
       TA	Average/Typical
       Fa	Fair
       NA	No Pool
       
```{r}
factorChart(train, "PoolQC", "SalePrice")
```
**Conclusion : ** Exceelent pool may help to deal with outliers.

###Fence###
**Fence:** Fence quality
		
       GdPrv	Good Privacy
       MnPrv	Minimum Privacy
       GdWo	Good Wood
       MnWw	Minimum Wood/Wire
       NA	No Fence

```{r}
factorChart(train, "Fence", "psf")
```

```{r}
factorChart(train, "Fence", "SalePrice")
```
**Conclusion : ** It may help to differentiate between good privacy and minimum privacy observations.

###MiscFeature###
**MiscFeature:** Miscellaneous feature not covered in other categories
		
       Elev	Elevator
       Gar2	2nd Garage (if not described in garage section)
       Othr	Other
       Shed	Shed (over 100 SF)
       TenC	Tennis Court
       NA	None

```{r}
factorChart(train, "MiscFeature", "psf")
```
**Conclusion : ** Almost all observation got NA except 54

###MiscVal###
**MiscVal:** $Value of miscellaneous feature
```{r message = FALSE}
contChart(train, "MiscVal", "SalePrice")
```
**Conclusion : ** Not Good
###MoSold### 
**MoSold:** Month Sold (MM)
```{r}
factorChart(train, "MoSold", "psf")
```
**Conclusion : Most of the transactions happended in may, june or july. Interesting!!!

###YrSold###
**YrSold:** Year Sold (YYYY)
```{r}
factorChart(train, "YrSold", "psf")
```
**Conclusion :** Almost no inflation. Need to join year and month to check.

###SaleType###
**SaleType:** Type of sale
		
       WD 	Warranty Deed - Conventional
       CWD	Warranty Deed - Cash
       VWD	Warranty Deed - VA Loan
       New	Home just constructed and sold
       COD	Court Officer Deed/Estate
       Con	Contract 15% Down payment regular terms
       ConLw	Contract Low Down payment and low interest
       ConLI	Contract Low Interest
       ConLD	Contract Low Down
       Oth	Other

```{r}
factorChart(train, "SaleType", "psf")
```
**Conclusion : ** Most of the observation got Conventional Warranty deed. New one are good.

###SaleCondition###
**SaleCondition:** Condition of sale

       Normal	Normal Sale
       Abnorml	Abnormal Sale -  trade, foreclosure, short sale
       AdjLand	Adjoining Land Purchase
       Alloca	Allocation - two linked properties with separate deeds, typically condo with a garage unit	
       Family	Sale between family members
       Partial	Home was not completed when last assessed (associated with New Homes)

```{r}
factorChart(train, "SaleCondition", "psf")
```
**Conclusion : ** Most of the sale are normal. Nothing evident.

###SalePrice###
```{r message = FALSE}
ggplot(train, aes(x = train[["SalePrice"]], y = ..density..)) +
      geom_histogram(fill = "red", alpha = 0.2, color = "black") +
      geom_density(fill = "green", alpha = 0.2)+
      labs(x = "SalePrice")
```

##Corelation Graph ##
```{r}
tokeep <- which(sapply(train,is.numeric))
M <- cor(train[ , tokeep, with=FALSE], use = "complete.obs")
row_indic <- apply(M, 1, function(x) sum(x > 0.3 | x < -0.3) > 1)
M<- M[row_indic ,row_indic ]
corrplot (M)
```
##Imputing Missing Values##
We know that pools are not present if null
```{r}
train[is.na(train$PoolQC)]$PoolQC = "No"
```
Same goes with MisFeature as well
```{r message = FALSE, error = FALSE, warning=FALSE}
train[is.na(train$MisFeature)]$MisFeature = "No"
```
and Alley
```{r}
train[is.na(train$Alley)]$Alley = "No"
```
and Fence
```{r}
train[is.na(train$Fence)]$Fence = "No"
```
Fireplaces too. If quality is not defined that means no fireplace.
```{r}
train[is.na(train$FireplaceQu)]$FireplaceQu = "No"
```
LotFrontage is quite complicated. As no info given in data dictonary. It may be in propotion with total lot area or may be 0. This one is really unknown. Let's assume those are 0 for now.
```{r}
train[is.na(train$LotFrontage)]$LotFrontage = 0
```

```{r}

```

```{r}

```

```{r}
train_nulls %>%
  filter(nulls > 0) %>%
  arrange(desc(nulls))
```

